Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks

### 2015-05-06 paper/paper.tex
Made final changes to paper.

\usepackage{setspace}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{verbatim}

\title{Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks}
\author{Michael Baraboo, William Schattgen, Christopher To}
\date{4 May 2015}
\begin{document}
\maketitle

@@

Phishing attacks are always developing and evolving, and one particular type of attack attempts to trick the user well after they have initially visited the site.  Coined by Firefox developer Aza Raskin in 2010, Tabnabbing is a specific phishing technique that relies on the user’s trust of websites they have already viewed and considered safe~\cite{Raskin}. Some users often leave many tabs open to return to interesting websites at a later time, and this behavior makes those users the perfect target for this type of attack. When the user has left a tab, a malicious website can detect that the user is not currently viewing that tab and change the content of that page. This is done using JavaScript or the HTML meta tag with a timer to rearrange the page at a time when the user is most likely not viewing it. The malicious site will typically attempt to change the page content, tab title, and favicon to appear as a login page for a familiar site such as Gmail or Facebook.  When the user returns to the tab, the changed page may request the user for their username and password, citing reasons such as an expired login session.  Because tabs are not expected to have changed while out-of-focus, and because users do not check URLs often, the site will seem legitimate and trustworthy.

@@

There are some preventative measures one can take to lower the risks of tabnabbing attacks.  Aza Raskin recommends using the Firefox Account Manager to prevent unwarranted credential release~\cite{Raskin}, but this can be cleverly overcome by loading the legitimate site and placing an identical but malicious form over the original form~\cite{NoTabNab}.  Many users recommend the browser extension NoScript, which stops JavaScript on every tab unless the site is whitelisted~\cite{NoTabNab}, but this extension is only available on Firefox, and the blanketed restriction of JavaScript may seem too extensive for some users.  There have been some applications that have developed specifically to combat tabnabbing, which will be explained through the following research.

@@

The authors do leave some issues of TabSol unaddressed in their paper.  First, the authors make the fundamental assumption that any tabnabbing page will have a login form.  This can be simply avoided by using a tabnabbing page that uses alternative means of communication such as a phone number, email address, or even a link to another login page.  The login form detection system will completely fail in detecting these types of phishing attacks.  Second, TabSol immediately and prematurely place any site that has matching hashes onto the whitelist, which could result in malicious sites being placed onto the whitelist.  If the user switches away and back to the tab before the malicious tab is scheduled to change, the tab will not change at all, and it will pass TabSol testing and be placed on the blacklist.  This login form basis and premature whitelisting can easily lead to the infiltration of tabnabbing sites.

@@

\section{Results}
The current build of Nabi restricts JavaScript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running JavaScript on that page. The page that is switched to is given access to run JavaScript and is also refreshed to reflect the change in permissions. This prevents JavaScript in the inactive tab from running while the user is not viewing it, but allows it to reactivate once the user returns. Because of this our strategy for defending against tabnabbing attacks allows the user to continue using the browser normally without the risk of running JavaScript in a background tab.

@@

Nabi successfully incorporates the first aspect of our proposal by changing the content settings with the Google Chrome browser to allow and disallow JavaScript dynamically whenever the user switches between tabs. However, Nabi does not yet incorporate a whitelist feature, thus all inactive tabs are forbidden from running JavaScript, reducing the capability to multitask within the browser. Thus the current system is more preventative of script-based tabnabbing attacks but less user-friendly. Lastly, Nabi does not yet detect the scriptless redirect attack and is therefore unable to prevent it or inform the user. The scriptless attack is less likely to succeed given that it must guess when the user will be looking away from the page. That makes this feature arguably less important than preventing the more effective script-based tabnabbing attack, but scriptless attack is dangerous nonetheless and its detection will be included in future development.

@@

\bibliographystyle{plain}
\bibliography{bibliography}

>>>>

\usepackage{setspace}
\usepackage[letterpaper,margin=1in]{geometry}
\usepackage{verbatim}
\usepackage{hyperref}

\title{Nabi - A Preventative Solution Against JavaScript and Scriptless Tabnabbing Attacks}
\author{Michael Baraboo, William Schattgen, Christopher To}
\date{7 May 2015}
\begin{document}
\maketitle

@@

Phishing attacks are always developing and evolving, and one particular type of attack attempts to trick the user well after they have initially visited the site.  Coined by Firefox developer Aza Raskin in 2010, Tabnabbing is a specific phishing technique that relies on the user's trust of websites they have already viewed and considered safe~\cite{Raskin}. Some users often leave many tabs open to return to interesting websites at a later time, and this behavior makes those users the perfect target for this type of attack. When the user has left a tab, a malicious website can detect that the user is not currently viewing that tab and change the content of that page. This is done using JavaScript or the HTML meta tag with a timer to rearrange the page at a time when the user is most likely not viewing it~\cite{Adler}. The malicious site will typically attempt to change the page content, tab title, and favicon to appear as a login page for a familiar site such as Gmail or Facebook.  When the user returns to the tab, the changed page may request the user for their username and password, citing reasons such as an expired login session.  Because tabs are not expected to have changed while out-of-focus, and because users do not check URLs often, the site will seem legitimate and trustworthy.

@@

There are some preventative measures one can take to lower the risks of tabnabbing attacks.  Aza Raskin recommends using the Firefox Account Manager to prevent unwarranted credential release~\cite{Raskin}, but this can be cleverly overcome by loading the legitimate site and placing an identical but malicious login form over the original login form~\cite{NoTabNab}.  Many users recommend the browser extension NoScript, which stops JavaScript on every tab unless the site is whitelisted~\cite{NoTabNab}, but this extension is only available on Firefox, and the blanketed restriction of JavaScript may seem too extensive for some users.  There have been some applications that have developed specifically to combat tabnabbing, which will be explained through the following research.

@@

The authors do leave some issues of TabSol unaddressed in their paper.  First, the authors make the fundamental assumption that any tabnabbing page will have a login form.  This can be simply avoided by using a tabnabbing page that uses alternative means of communication such as a phone number, email address, or even a link to another login page.  The login form detection system will completely fail in detecting these types of phishing attacks.  Second, TabSol immediately and prematurely places any site that has matching hashes onto the whitelist, which could result in malicious sites being placed onto the whitelist.  If the user switches away and back to the tab before the malicious tab is scheduled to change, the tab will not change at all, and it will pass TabSol testing and be placed on the blacklist.  This login form basis and premature whitelisting can easily lead to the infiltration of tabnabbing sites.

@@

\section{Results}
The current build of Nabi restricts JavaScript from running in every tab the user has switched from. The tab is then refreshed to reflect those restrictions and to the cancel the actively running JavaScript on that page. The page that is switched to is given access to run JavaScript and is also refreshed to reflect the change in permissions. This prevents JavaScript in the inactive tab from running while the user is not viewing it, but allows it to reactivate once the user returns. Because of this, our strategy for defending against tabnabbing attacks allows the user to continue using the browser normally without the risk of running JavaScript in a background tab.

@@

Nabi successfully incorporates the first aspect of our proposal by changing the content settings with the Google Chrome browser to allow and disallow JavaScript dynamically whenever the user switches between tabs. However, Nabi does not yet incorporate a whitelist feature, thus all inactive tabs are forbidden from running JavaScript, reducing the capability to multitask within the browser. As a result, the current system is more preventative of script-based tabnabbing attacks but less user-friendly. Lastly, Nabi does not yet detect the scriptless redirect attack and is therefore unable to prevent it or inform the user. The scriptless attack is less likely to succeed given that it must guess when the user will be looking away from the page. That makes this feature arguably less important than preventing the more effective script-based tabnabbing attack, but scriptless attack is dangerous nonetheless and its detection will be included in future development.

@@

\raggedright
\bibliographystyle{plain}
\bibliography{bibliography}
